Homework

### 2016-07-04 Macro Impacts.tex
Last notes before I sleep.
Small correction to units.

$\bar p$ can be taken to be the maximum stress such that the elastic limit holds i.e. the elastic limit. Some reading suggests that this is about 13 GPa. $K$ and $\lambda+2\mu$ can be taken to be on the order of $10^{10}$ GPa (obviously we should look into this). $\Delta r$ should be very small, on the order of the radius of the macro. $\lambda_0$ is about $6$ to $10$ kilometers, and is the wavelength at which modes propagate without significant attenuation. $r_0$ can be determined by geometric means. A first guess yields

@@

This is within one order of magnitude of the answer gotten from (24). Note, my estimate for $r_0$ turned out to be about 1 kilometer. I'm still not entirely sure of the correct way to calculate $r_0$.

>>>>

$\bar p$ can be taken to be the maximum stress such that the elastic limit holds i.e. the elastic limit. Some reading suggests that this is about 13 GPa. $K$ and $\lambda+2\mu$ can be taken to be on the order of $10^{10}$ Pa (obviously we should look into this). $\Delta r$ should be very small, on the order of the radius of the macro. $\lambda_0$ is about $6$ to $10$ kilometers, and is the wavelength at which modes propagate without significant attenuation. $r_0$ can be determined by geometric means. A first guess yields

@@

This is within one order of magnitude of the answer gotten from (24). Note, my estimate for $r_0$ turned out to be about 1 kilometer. I'm still not entirely sure of the correct way to calculate $r_0$. If we take $\bar p\approx 10^{8}$ Pa, then $\Xi\approx 10^{-10}$. That said, it's 2:00 am and I'm doing these estimates in my head, so don't take any of this too seriously. The only really important thing is the idea that we can ignore the non-linear evolution since we can reasonably guess its end state and assume no energy loss in between.
